---
title: "mitology R package"
output: 
    github_document:
        toc: false
        toc_depth: 2
        fig_width: 5
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<img src=./vignettes/figures/puzzle_mitology.png width="200" align="right" />

Mitology is an R package to dissect mitochondrial activity from gene expression data. We provide in R environment MitoCarta3.0 pathways and we exploited Reactome pathways and GO hierarchies to derive and re-organize mitochondrial-specific gene sets. 

## Installation

The `mitology` package can be installed from Bioconductor:

```{r, eval = FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("mitology")
```

Also you can install the latest version of `mitology` from GitHub with:

```{r, eval=FALSE, message=FALSE}
library(remotes)
remotes::install_github("CaluraLab/mitology")
```

